Which Scenario Should We Design For? Insights from House Elevation on the Multiple PDF Problem

### 2021-10-21 papers/operationalizing-bayesian-checking.tex
Klaus Edits

% TO DO NOTES
\usepackage{xcolor} % list of colors at https://en.wikibooks.org/wiki/LaTeX/Colors
\definecolor{giallo}{HTML}{F0BC42} % https://teamcolorcodes.com/a-s-roma-color-codes/
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\usepackage[textsize=scriptsize]{todonotes}
\setlength{\marginparwidth}{1.75in}
\newcommand{\james}[1]{\todo[color=giallo, textcolor=nero]{\textbf{ATTN James:~}#1}} % if desired create a custom command for each author
\newcommand{\klaus}[1]{\todo[color=rosso, textcolor=grigio]{\textbf{ATTN Klaus:~}#1}}

@@

\paragraph{Set up the ``Multiple PDF Problem''}
While classical utility- or regret-based frameworks offer a structure for weighing these risks, they are not designed to handle uncertainties that are \emph{deep} in the sense that stakeholders may not agree upon their probabilities \citep{lempert_complex:2002} or \emph{irreducible} in the sense that there is not an objective truth that better models and data can identify \citep{DossGollin:2019}.\footnote{Unless we believe everything is pre-determined, in which case why bother with climate adaptation\ldots}
Examples of such uncertainties include how much greenhouse gasses humans will emit in the future or whether the U.S. federal government will continue to subsidize flood insurance for homeowners\james{Add some references -- Klaus suggests \citet{savage:1954} or similar}.
In response, a wide range of fields have developed scenario-based methods\ldots.
This leads to the ``Multiple PDF Problem'' \citep{sharma_rcp:2021}\ldots.
A key question, then, facing the designers, builders, regulators, owners, and users of built facilities is \emph{to which scenario should infrastructure be designed?}

>>>>

% TO DO NOTES
\usepackage{xcolor} % list of colors at https://en.wikibooks.org/wiki/LaTeX/Colors
\definecolor{giallo}{HTML}{F0BC42} % https://teamcolorcodes.com/a-s-roma-color-codes/
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\usepackage[textsize=scriptsize]{todonotes}
\setlength{\marginparwidth}{1.5in}
\newcommand{\james}[1]{\todo[color=giallo, textcolor=nero]{\textbf{ATTN James:~}#1}} % if desired create a custom command for each author
\newcommand{\klaus}[1]{\todo[color=rosso, textcolor=grigio]{\textbf{ATTN Klaus:~}#1}}

@@

\paragraph{Set up the ``Multiple PDF Problem''}
While classical utility- or regret-based frameworks offer a structure for weighing these risks, they are not designed to handle uncertainties that are \emph{deep} in the sense that stakeholders may not agree upon their probabilities \citep{lempert_complex:2002} or \emph{irreducible} in the sense that there is not an objective truth that better models and data can identify \citep{DossGollin:2019}.\footnote{Unless we believe everything is pre-determined, in which case why bother with climate adaptation\ldots}
Examples of such uncertainties include how much greenhouse gasses humans will emit in the future or whether the U.S. federal government will continue to subsidize flood insurance for homeowners.\james{Add some references}
In response, a wide range of fields have developed scenario-based methods\ldots.\klaus{Which arguments in \citet{savage:1954} did you think should be cited here?}
This leads to the ``Multiple PDF Problem'' \citep{sharma_rcp:2021}\ldots.
A key question, then, facing the designers, builders, regulators, owners, and users of built facilities is \emph{to which scenario should infrastructure be designed?}
